\documentclass[11pt, oneside]{book}
\usepackage{geometry}       
\usepackage[parfill]{parskip} 
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{emptypage}
\usepackage{courier}
\usepackage{wrapfig}
\usepackage{listings}% http://ctan.org/pkg/listings
\usepackage[colorlinks=true, pdfstartview=FitV, linkcolor=blue,
            citecolor=blue, urlcolor=blue]{hyperref}
\geometry{letterpaper}   
\lstset{basicstyle={\small\ttfamily},mathescape}
\pagenumbering{arabic}

\newcommand{\lean}[1]{\texttt{#1}}


% ------------------- Title and Author -----------------------------
\title{Using LEAN Theorem Prover to Teach Formal Mathematics:
Lean-Intro-Topology Library}
\author{Rafael Grenier}
\begin{document}


\frontmatter
\maketitle
\newpage
{
  \vfill
  \LARGE 
  \textbf{Abstract}
  \normalsize

  Interactive theorem provers have become more popular in recent
  years within the field of mathematics, since theorem provers provide
  guarantees of the validity of proofs. Even more
  recently, there have been pushes to use theorem provers in the
  classroom to aid in teaching formal mathematics to undergraduate 
  students. Students and instructors alike benefit from the certainty
  provided by the theorem prover, as students can develop a precise
  logical foundation and receive immediate feedback, and instructors 
  can instantly grade their students' proofs. In 2022, Dr. Kevin Buzzard 
  pioneered a course at Imperial College London in formal mathematics
  using the Lean theorem prover \cite{Buzzard}, and some
  other universities have followed suit with similar programs.
  Continuing in this effort to use theorem provers for teaching mathematics,
  I have developed a library of Lean code entitled 
  ``\href{https://github.com/rafaelgrenier/lean-intro-topology/}{Lean-Intro-Topology}''
  with explanations and exercises designed to guide students through 
  formal reasoning and basic set theory, then practice using that newly
  acquired knowledge to prove some theorems in point-set topology.
  This code library has already seen some academic use as a supplemental
  resource for a graduate-level course in Spring 2024
  on formalizing mathematics at the University of Arizona, which my 
  thesis mentor Dr. Sergey Cherkis taught and I assisted. 
  This paper describes the inspiration for creating my code library, 
  its contents, its development process, and the insights I gathered
  while working on the library and as a teaching assistant.

  \vfill
}
\tableofcontents

\mainmatter
\include{Chapter1/chapter1}
\include{Chapter2/chapter2}
\include{Chapter3/chapter3}
\bibliographystyle{IEEEtran}
\bibliography{mybibliography}


\end{document}
\end
